Enhancement of Speech Recognition Results Using Server-side Post-processing

### 2019-06-23 none_cloud_post_processing_decoding/doc/main.tex
Updates figures

Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
system and the server-side post processing system. 
The symbols used in this figure is defined as follows:
%
\begin{align}
  \vec{x}[m]:& \quad \text{Acoustic feature vector from speech.}  \nonumber \\
  \hat{y}_o[l]:& \quad \text{The frame-synchronous hypothesis from the
  on-device speech recognizer.}   \nonumber \\
       & \quad \hat{y}_o[l] \in \mathbb{V}.  \nonumber \\
  \hat{y}_o[0:l+1]  : & \quad \text{The sequence of $y[l']$ where } 0 \le l'
  \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
  \hat{y}_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
  \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
  W_i: & \quad \text{The word sequence. } W_i \in  \mathbb{D}.  \nonumber 
\end{align}
where $\mathbb{V}$ is the set of grapheme symbols, and $\mathbb{D}$ is the
set of words. In Fig. \ref{fig:entire_system}, there are two top level
blocks. The left and right blocks correspond to processing on the local
device and the server side post processing respectively.

\subsection{Label Likelihood Calculation}
To perform decoding described in Section \ref{sec:decoding}, 
we need to calculate likelihood $P(y[0:l+1] |z[l])$
where $\mathcal{Y}[0:l]$ is the 
In this block, the objective is to calculate the likelihood
of the on-device ASR output $\mathcal{Y}[0:l]$ depending on 
the label $z[l]$, which may be mathematically given
by
\begin{align}
  P(\hat{y}_o[0:l+1] \big| \hat{y}_p[l]) 
    = \frac{P(\hat{y}_p[l] \big| \hat{y}_o[0:l+1])
        P\left(\hat{y}_o[0:l+1] \right)}{P(\hat{y}_p[l])}
  \label{eq:post_prob}
\end{align}

\subsection{Decoding}
\label{sec:decoding}
The structure of the post-processing decoder is depicted in Fig.
\ref{post_processing_decoder}. Using the dictionary and the
language model, the hypothesis word sequence $W_i$ is obtained
from the posterior probability in \eqref{eq:post_prob}.

@@

\section{Feedback Sequence Classifier}
\label{sec:feedback_sequence_classifier}

\subsection{Neural Network Structure}
\label{sec:neural_network_structure}
Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
Speech features $\vec{x}[m]$ are sampled 
at every 10 {\it ms}, which is the usual frame period in speech 
\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00}.
As shown in this figure, LSTM layers and max-pool layers
are interleaved from the bottom layer up to the third max-pool layer.
Using three 2:1 max-pool layers, the softmax output $\vec{z}[u]$ has 
a frame period of 80 {\it ms}.  Thus, the relationship between the original frame 
index $m$ and the temporal sub-sampled index $u$ is given by \eqref{eq:def_u_U}.
The relationship between the length of the softmax output sequence $U$
and the length of the feature sequence $M$ is also given in the same way:
	\begin{align}
		u = \lceil m / 8 \rceil,  \; U = \lceil M / 8 \rceil \label{eq:def_u_U}.
	\end{align}

FSC performs inference in a frame-synchronous way as described in 
Sec. \ref{sec:frame_synchronous_inference}. 
However, due to this temporal sub-sampling, the latent label sequence 
in \eqref{eq:latent_label_seq} is slightly modified as shown below:
\begin{align}
  \mathcal{Z}[0:U]  =  
    \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
  \label{eq:subsampled_latent_label_seq}
\end{align}

The loss function 
$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ 
is also modified from the original one in 
\eqref{eq:frame_synchronous_ce_loss}:
\begin{align}
	\mathbb{L}_{\text{fsc}}
    \left(\mathcal{X}[0:M], \mathcal{Z}_{0:U}\right)
      = \sum_{u=0}^{U-1}  
          \sum_{v=0}^{V-1}
          {(\vec{z}[u])_v}  \log ( 
             \widehat{\vec{z}}[u] )_v  
        \label{eq:fsc_ce_loss} 
\end{align}
The reason for performing the 8:1 temporal sub-sampling in \eqref{eq:def_u_U} is to 
to make the period of the softmax output $\widehat{\vec{z}}[u]$ in \label{eq:fsc_ce_loss} 
be similar to the shortest BPE duration. We assume that the {\it sequence-to-sequence}
neural network models will be trained most efficiently when the period of neural 
network output roughly matches the period of the target. In addition, this
output periods must be equal to larger than the shortest target period to prevent
missing some targets.
The shortest duration of each BPE is similar to the average length of {\it phones}, 
which is any distinct speech sound serving as a phonetic unit.
It has been observed that the average phone duration is between 50 {\it ms}
\textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.
Under this rationale, we chose the temporal sub-sampling factor of 8:1. 
We also observe this sub-sampling factor is optimal in our experiments as well.

\subsection{Target units of Feedback Sequence Classifier}
\label{sec:target_units}

In FSC, we use subword units created by BPE \cite{r_sennrich_acl_2016_00} for
the output vocabulary $\mathbb{V}$ in 
\eqref{eq:transformation} and \eqref{eq:subsampled_latent_label_seq}.

When creating the latent frame-wise label sequence $\mathcal{Z}[0:U]$ 
in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
from other frames.  For example, if we have a BPE unit
("{\it an}") in the vocabulary $\mathbb{V}$, then we define another
target ("{\it an$_o$}") which marks the on-set frame of this BPE
interval. Thus, when the number of BPE units is $B$, the total
number of vocabularies in $\mathbb{V}$ becomes $2B$.
We refer this approach to as {\it BPE with onset marking}.

The reason for using this approach is two-folds. First, since FSC
generates an inference output for each frame, if the same
BPE symbol repeatedly appears, it is difficult to tell whether 
this BPE is really expected to appear multiple times or whether 
the a single BPE is continuing. For example, when we have 
a sequence \{"{\it an}", "{\it an} "\}
as the inference output, it is difficult to tell whether it should be a single
"{\it an}" or two "{\it an}"s. With the onset marking,
a decoder needs to print out the inference outputs with onset marking. 
The blank symbol in CTC also plays a similar role. However this blank symbol
is a common symbol following any labels. In the FSC algorithm, the information
given by the feedback paths is crucial in performance. In this aspect,
blank symbol is not very useful for this feedback structure. 
Second, we have frequently observed that the on-set portion of sound
has a very important role in human auditory perception 
\cite{C_Kim_INTERSPEECH_2014_2}.

\subsection{Training of the Feedback Sequence Classifier}
In this section, we describe how to train FSC.  Algorithm 
\ref{algo:fsc_training} shows how FSC is trained using the 
$N$-best alignment algorithm and the cross entropy loss function. 
$N$-best algorithm will be described 
in Sec. \ref{sec:n_best_alignment} in detail.
In Algorithm \ref{algo:fsc_training}  
As mentioned in Sec. 
\ref{sec:frame_synchronous_inference}, FSC performs inference
in a frame-synchronous way.
The first step is making an 
In this section, we describe how to train FSC. The first step is 
is to make an alignment using the $N$-best alignment. The second step is updating the
neural network parameters using the Cross Entropy (CE) criterion.

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}[0:M]$.

\begin{algorithm}
  \caption{Training procedure for the FSC algorithm}
  \label{algo:fsc_training}
  \begin{algorithmic}
    \State $\Theta^{(0)} \leftarrow$ initialize\_parameters()
    \For {epoch index $i = 0, . . . , I-1$}
      \For {each batch $\left\{\mathcal{X}[0:M],
                        \mathcal{Y}_{0:L}  \right\}$}, 
        \State $ {{\mathcal{Z}^{(i)}}[0:U]}
          \leftarrow
          \text{n\_best\_align}
          \left(
            \mathcal{X}[0:M] \Big| \Theta^{(i)}
          \right)$

        \State {$\Theta^{(i)} \leftarrow$ update\_parameter 
          $\left(
            \mathcal{X}[0:M],
            \mathcal{Z}^{(i)}[0:U]
          \right)$}

    \EndFor
    \State $\Theta^{(i+1)} := \Theta^{(i)}$
  \EndFor
  \label{algorithm:fsc_training}
  \end{algorithmic}
\end{algorithm}

\subsection{N-best alignment}
\label{sec:n_best_alignment}

In CTC in Sec. \ref{sec:ctc} and in RNN-T in Sec. \ref{sec:rnn_t}, the 
forward-backward algorithm is employed to update parameters. 
For example in CTC, the forward-backward algorithm is based on the
following assumption:
\begin{align}
  P \left(  \Big| \right) = \Pi
\end{align}

In conventional frame-wise CE-training, Viterbi alignment 
(a.k.a forced alignment) has been performed to obtain the frame-level 
acoustic unit  boundaries TODO(chanwcom). Even though the Viterbi algorithm
has advantages in simplicity and efficiency, it is based on
the following conditional independence assumption.

In FSC, we propose the following $N$-best alignment approach rather than
the Viterbi alignment algorithm to find the alignment information.

TODO(chanw.com) Define $f$.

>>>>

Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
system and the server-side post processing system. In this figure,  
the two top level blocks on the left and the right hand sides correspond
to {\it speech recognition on the local device} and 
{\it post processing on the server} respectively.  The symbols used in this 
figure is defined as follows:
%
\begin{align}
  \vec{x}[m]:& \quad \text{Acoustic feature vector from speech.}  \nonumber \\
  \hat{y}_o[l]:& \quad \text{The frame-synchronous hypothesis from the
  on-device speech recognizer.}   \nonumber \\
       & \quad \hat{y}_o[l] \in \mathbb{V}.  \nonumber \\
  \hat{y}_o[0:l+1]  : & \quad \text{The sequence of $y[l']$ where } 0 \le l'
  \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
  y_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
  \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
  W_i: & \quad \text{The word sequence. } W_i \in  \mathbb{D}.  \nonumber 
\end{align}
where $\mathbb{V}$ is the set of grapheme symbols, and $\mathbb{D}$ is the
set of words. In Fig. \ref{fig:entire_system}, there are two top level
blocks. The left and right blocks correspond to processing on the local
device and the server side post processing respectively.

\subsection{Label Likelihood Calculation}
To perform decoding described in Section \ref{sec:decoding}, 
we need to calculate likelihood $P(\hat{y}_o[0:l+1] | y_p[l])$
where $\hat{y}_o[0:l+1]$ is the sequence of the frame-synchronous 
label hypothesis.
Using the Bayes rule, this likelihood is expressed in the following form:
\begin{align}
  P(\hat{y}_o[0:l+1] \big| y_p[l]) 
    = \frac{P(y_p[l] \big| \hat{y}_o[0:l+1])
        P\left(\hat{y}_o[0:l+1] \right)}{P(y_p[l])}.
  \label{eq:likelihood_prob}
\end{align}
To calculate the above equation, the following three terms need to be
calculated:
\begin{align}
  P(y_p[l] \big| \hat{y}_o[0:l+1]): & \text{ A posterior probability of } y_p[l]
    \text{ given the frame-synchronous label sequence } \nonumber \\ 
    & \hat{y}_o[0:l+1].
    \nonumber \\
  P\left(\hat{y}_o[0:l+1] \right): & 
    \text{ A probability of the sequence of frame-synchronous labels } \hat{y}_o[0:l+1].
      \nonumber \\
  P(y_p[l]): & \text{ A prior probability of the label } y_p[l] \in \mathbb{V}.
  \label{eq:prob_components_likelihood}
\end{align}

To calculate $P\left(\hat{y}_o[0:l+1] \right)$ in \eqref{eq:likelihood_prob}, 
we use a either statistical n-gram or a RNN based Language Model (LM). 
One notable difference of the LM used for this purpose compared 
to a conventional LM is that this LM must be a frame-synchronous LM.
and must be trained from frame-synchronous label corpus. 
Thus, we first need to align transcribed speech corpus to obtain frame-synchronous 
labels and train LM from this corpus. 
Finally, we use this LM to calculate $P\left(\hat{y}_o[0:l+1] \right)$.

Instead of calculating the likelihood of the whole sequence 
$\hat{y}_o[0:l+1]$ described above, a simpler alternative is to ignore
the past values of the original hypothesis $\hat{y}_o[0:l+1]$ and only to
consider the current one $\hat{y}_o[l]$. Under this simplification,
the likelihood in \eqref{eq:likelihood_prob} may be simplified as follows:
\begin{align}
  P(\hat{y}_o[l] \big| y_p[l]) 
    = \frac{P (y_p[l] \big| \hat{y}_o[l]) P(\hat{y}_o[l])}{P(y_p[l])} 
\end{align}

\subsection{Decoding}
\label{sec:decoding}
The structure of the post-processing decoder is depicted in Fig.
\ref{fig:post_processing_decoder}. Using the dictionary and the
language model, the hypothesis word sequence $W_i$ is obtained
from the posterior probability in \eqref{eq:post_prob}.

@@
